TODO title

### 2017-01-13 doc/paper/paper.tex
Start creating figures.

\usepackage{cogsci}
\usepackage{commath}
\usepackage{pslatex}
\usepackage{apacite}

@@

TODO figure with dynamics

@@

TODO figure with dynamics

@@

We find that the ability to reach a clear decision depends on the magnitude of 
the highest input for both networks. This is not surprising. In the 
Usher-McClelland the output magnitude will be determined by the input magnitude 
of the largest input. As such the largest input needs to be above 0.2 to fulfill 
the requirements. For the independent accumulator model the input has to be 
large enough to reach the integration threshold within the time limit. By 
increasing the input scaling $\lambda$ or the time limit one could get a clear 
decision for smaller inputs within the time limit. We further find that the 
independent accumulator model is independent of the input noise and target 
separation for all tested parameters. This is not the case for the 
Usher-McClelland model as shown in Figure~TODO where the fraction of trials 
without a clear decision increases with noise and smaller target separation.

However, when considering the correctness of the decisions (Figure~TODO) the 
Usher-McClelland model is doing better. We can alleviate that difference to some 
degree by reducing the input scaling to $\lambda = TODO$, but perform still 
worse for small target separations when staying in the time limit.

@@

TODO\@: distribution of neurons in network, looking only at cases where 
a decision could be made within the results.

>>>>

\usepackage{cogsci}
\usepackage{commath}
\usepackage{graphicx}
\usepackage{pslatex}
\usepackage{apacite}

@@

TODO figure with dynamics
\begin{figure}
    \centering
    \includegraphics{figures/usher-mcclelland}
    \caption{TODO}\label{fig:usher-mcclelland}
\end{figure}

@@

TODO figure with dynamics
\begin{figure}
    \centering
    \includegraphics{figures/indacc}
    \caption{TODO}\label{fig:indacc}
\end{figure}

@@

We find that the ability to reach a clear decision depends on the magnitude of 
the highest input for both networks. This is not surprising. In the 
Usher-McClelland the output magnitude will be determined by the input magnitude 
of the largest input. As such the largest input needs to be above 0.2 to fulfill 
the requirements. For the independent accumulator model the input has to be 
large enough to reach the integration threshold within the time limit. By 
increasing the input scaling $\lambda$ or the time limit one could get a clear 
decision for smaller inputs within the time limit. We further find that the 
independent accumulator model is independent of the input noise and target 
separation for all tested parameters. This is not the case for the 
Usher-McClelland model as shown in Figure~TODO where the fraction of trials 
without a clear decision increases with noise and smaller target separation.
\begin{figure}
    \centering
    \includegraphics{figures/decisions}
    \caption{TODO}\label{fig:decisions}
\end{figure}

However, when considering the correctness of the decisions (Figure~TODO) the 
Usher-McClelland model is doing better. We can alleviate that difference to some 
degree by reducing the input scaling to $\lambda = TODO$, but perform still 
worse for small target separations when staying in the time limit.
\begin{figure*}
    \centering
    \includegraphics{figures/correct}
    \caption{TODO}\label{fig:correct}
\end{figure*}

@@

TODO\@: distribution of neurons in network, looking only at cases where 
a decision could be made within the results, what about more choices, include 
a number of parameters and github url.
